Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-12-29 awipev-CO2.Rmd
Merge nutrient data

# The nearest times
time_index <- unique(d_all$datetime)
# nuts$closest <- time_index[
#   FNN::knnx.index(time_index, # The values to be queried (big df)
#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
#                   k = 1)] # The number of closest values to return
nuts <- nuts %>% 
  dplyr::mutate(closest = time_index[
  FNN::knnx.index(time_index, # The values to be queried (big df)
                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
                  k = 1)]) %>%  # The number of closest values to return
  dplyr::select(-date, -datetime) %>% 
  dplyr::rename(NO3NO2 = `NO3+NO2`)
tmp <- left_join(d_all, nuts, by = c("datetime" = "closest"))

```
```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

>>>>

# The nearest times
time_index <- unique(d_all$datetime)
# nuts$closest <- time_index[
#   FNN::knnx.index(time_index, # The values to be queried (big df)
#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
#                   k = 1)] # The number of closest values to return
nuts <- nuts %>% 
  dplyr::mutate(closest = time_index[
  FNN::knnx.index(time_index, # The values to be queried (big df)
                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
                  k = 1)]) %>%  # The number of closest values to return
  dplyr::select(-date, -datetime) %>% 
  dplyr::rename(NO3NO2 = `NO3+NO2`)
d_all <- left_join(d_all, nuts, by = c("datetime" = "closest"))
```
```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
